To Do List

### 2018-09-19 Manuscript/results_outline.Rmd
updated

>>>>

* GM12878 Resuts
   + How many total genomic bins
   + How many total TADs
      - Summary stats for lengths of TADs
   + Total number of features 
      - Summary stats for both counts and distance features
      - Which features were removed for near zero variance
   + Normalization Techniques
   + Class balancing techniques
   + Variable selection techniques
   + Final Models
      - Mourad Models (MLR & LASSO)
      - Models using distance/counts features with out pipeline (MLR & LASSO)
      - Elastic-Net using processed data
      - Comparisons
* Validate results using K562 cell line
* Validate results using TFBS cell line

# Discussion

* State the results that were interesting 
   - Specific to each cell line/tfbs
   - Then results all together
* State how much better models using our pipeline performed compared to Mourad
   - Was it due to the model choice or the use of distance features?
* Limitations/Future
   - Mention the need for HiC experiments using higher resolutions
   - Experimenting with TAD data using other methods
   - Exploring other cell lines

### 2018-09-19 ToDo.Rmd
updated

*Make a bullet pointed list for manuscript
*Apply RF, GBM, SVM (later), MLR using our features
*Finish Methods
*Finish running code applied to 100 iterations of undersampling
*Apply pipeline to K562 cell line

>>>>

+ Make a bullet pointed list for manuscript
+ Apply RF, GBM, SVM (later), MLR using our features
+ Finish Methods
+ Finish running code applied to 100 iterations of undersampling
+ Apply pipeline to K562 cell line

* Should figures be placed in back of paper (in Appendix section)?
* Line 60 of manuscript: Check for accuracy?

+ in table with total features put (*) for removed then state why
+ order figures and create legends
* Finish results outline
* Finish results manuscript

## 09/17/18

* clustered vs cell type specific tfbs
   +/home/sequencing/data/ExtData/db_5.00_07-22-2015/grsnp_db/hg19/ENCODE/

* Finish TFBS models
* Include column for feature table for why a feature was excluded
* Use tables instead of barplots for performance metrics
* class imbalance barplot unnecessary, put in words
* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
* put tad in boundary before tad not in boundary for class imbalance table
* include venn diagram of selected features
* create a heat map for AIC values from commonly selected features
* look at chromosome specific models and compare
* look at different resolutions (talk with john)
* look at other type of transformation (inverse sine transformation)
